Assessing Usability of Tor Browser

### 2015-04-10 PETS2015-paper/paper.tex
Add descriptions to resources.

\url{https://blog.torproject.org/blog/ux-sprint-2015-wrapup}

\url{https://trac.torproject.org/projects/tor/wiki/org/meetings/2015UXsprint}

\url{https://people.torproject.org/~dcf/uxsprint2015/}

>>>>

These are online artifacts of our completed pilot study.

\noindent \url{https://trac.torproject.org/projects/tor/wiki/org/meetings/2015UXsprint}\\
\noindent \url{https://blog.torproject.org/blog/ux-sprint-2015-wrapup}\\
\indent Summary and results of the study.

\noindent \url{https://people.torproject.org/~dcf/uxsprint2015/}\\
\indent Subtitled screen recordings.
